Democracy, Public Support, and Measurement Uncertainty

### 2021-05-05 paper/dcpo_demsupport.Rmd
using saveRDS to prevent unsuccessful saving

save(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

save(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

@@

# the readRDS produced "unknown format" error, very weild
# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

@@

save(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

save(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

@@

#save(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

save(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

@@

save(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

@@

save(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```

>>>>

saveRDS(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

@@

# the readRDS produced "unknown format" error, very weild
# saveRDS(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

@@

saveRDS(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

@@

#saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

@@

saveRDS(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

@@

saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```
